quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-09-01 paper-quollr.Rmd
Updated threshold
Updated scaling data section

The algorithm starts by scaling the NLDR data to to the range $[0, 1] \times [0, x_2]$, where $x_2$ is the maximum value of the second embedding, using the `gen_scaled_data()` function. The output includes the scaled NLDR data (`scaled_nldr`) along with the original limits of the embeddings (`lim1`, `lim2`).

@@

For simplicity, we remove low-density hexagons using a threshold of $10$.

>>>>

The algorithm starts by scaling the NLDR data to to the range $[0, 1] \times [0, y_{2,max}]$, where $y_{2,max} = r_2/r_1$ is the ratio of ranges of embedding components. The output includes the scaled NLDR data (`scaled_nldr`) along with the original limits of the embeddings (`lim1`, `lim2`).

@@

For simplicity, we remove low-density hexagons using a threshold of $1$.
